### 2009-12-11 docs/marcello-dissertation/thesis/chapter4-netbeams-in-depth-requirements-analysis-and-specification.tex
Revision of Prof. Puder's audio feedback of chapter 5, as well as entire restructure of the document, such as using more page width and height, making it more visual. Table references not working automatically, as well as page numbers (will review later). Table references are entered manually in the text.
The structure of chapter 5 changed according to the fact that some
sections, subsections were very short, with 1 paragraph. So, I decided
to use two different options:

* If there are more to be discussed, a new advantages/disadvantages
subsection is created; or else, one section includes two

\begin{figure}[!t]
  \centering
    \includegraphics[scale=0.7]{../diagrams/cam_image-oct15}
  \caption{Picture of the SF-BEAMS Network, at the RTC pier. Tiburon, CA.}
  \label{fig:sf-beams}
\end{figure}

@@

\begin{figure}[!b]
  \centering
  \includegraphics[scale=0.5]{../diagrams/SF-BEAMS-system-architecture}
  \caption{The Current SF-BEAMS Data Collection Process}
  \label{fig:SF-BEAMS-system-architecture}
\end{figure}

@@

\begin{figure}[!b]
  \centering
  \includegraphics[scale=0.7]{../diagrams/ysi-device}
  \caption{Picture of the case study Sonde device: YSI 6600 ESD V2}
  \label{fig:ysi-device}
\end{figure}

@@

Considering the infrastructure, the data load in the server-side
of RTC's laboratories produced by the YSI Sonde sensors devices can be
estimated by analyzing the data distribution over a period of one year, as
shown in Table \ref{tab:year-data-distribution}.

\begin{table}[!b]
    \label{tab:year-data-distribution}
     \begin{center}
      \begin{tabular}{|c|c|c|c|c|c|c|}\hline 
        \textbf{\# of YSIs} & \textbf{Rate} & \textbf{Hourly} &
        \textbf{Daily} & \textbf{Weekly} & \textbf{Monthly} & \textbf{Yearly}\\\hline 
        1 & 1 min & 3.04 Kb & 73.12 Kb & 511.87 Kb & 1.99 Mb & 23.99 Mb\\\hline 
        5 & 6 min & 15.23 Kb & 365.62 Kb & 2.5 Mb & 9.99 Mb & 119.97 Mb\\\hline 
        1 & 15 min & 0.5 Kb & 12.18 Kb & 85.31 Kb & 341.25 Kb & 3.99 Mb\\\hline 
        5 & 1 min & 2.54 Kb & 60.93 Kb & 426.56 Kb & 1.67 Mb & 19.99 Mb\\\hline
        1 & 6 min & 0.2 Kb & 4.87 Kb & 34.12 Kb & 136.5 Kb & 1.6 Mb\\\hline 
        5 & 15 min & 1.0 Kb & 24.37 Kb & 170.62 Kb & 682.5 Kb & 7.99 Mb\\\hline
        \end{tabular}
        \caption{Estimated data volume produced by the RTC's YSI sondes}
      \end{center}
\end{table}

@@

In conclusion, after detailing the SF-BEAMS sensor network, and describing the 
infrastructure of NetBEAMS, its the motivation and goals for this project were 
presented. The next chapter is the actual analysis of existing database systems 
mentioned in Chapter 2, which aligns with the requirements and characteristics of 
NetBEAMS. Meanwhile, more details regarding the architecture of NetBEAMS, as well as
the development guidelines can be found in the appendix of chapter 10.

>>>>

\begin{figure}[!b]
  \centering
    \includegraphics[scale=0.7]{../diagrams/cam_image-oct15}
  \caption{Picture of the SF-BEAMS Network, at the RTC pier. Tiburon, CA.}
  \label{fig:sf-beams}
\end{figure}

@@

\begin{figure}[!h]
  \centering
  \includegraphics[scale=0.5]{../diagrams/SF-BEAMS-system-architecture}
  \caption{The Current SF-BEAMS Data Collection Process}
  \label{fig:SF-BEAMS-system-architecture}
\end{figure}

@@

\begin{figure}[!h]
  \centering
  \includegraphics[scale=0.7]{../diagrams/ysi-device}
  \caption{Picture of the case study Sonde device: YSI 6600 ESD V2}
  \label{fig:ysi-device}
\end{figure}

@@

Considering the infrastructure, the data load in the server-side
of RTC's laboratories produced by the YSI Sonde sensors devices can be
estimated by analyzing the data distribution over a period of one year, as
shown in Table 4.1.

\begin{table}[!h]
    \label{tab:year-data-distribution}
     \begin{center}
      \begin{tabular}{|c|c|c|c|c|c|c|}\hline 
        \textbf{\# of YSIs} & \textbf{Rate} & \textbf{Hourly} &
        \textbf{Daily} & \textbf{Weekly} & \textbf{Monthly} & \textbf{Yearly}\\\hline 
        1 & 1 min & 3.04 Kb & 73.12 Kb & 511.87 Kb & 1.99 Mb & 23.99 Mb\\\hline 
        5 & 6 min & 15.23 Kb & 365.62 Kb & 2.5 Mb & 9.99 Mb & 119.97 Mb\\\hline 
        1 & 15 min & 0.5 Kb & 12.18 Kb & 85.31 Kb & 341.25 Kb & 3.99 Mb\\\hline 
        5 & 1 min & 2.54 Kb & 60.93 Kb & 426.56 Kb & 1.67 Mb & 19.99 Mb\\\hline
        1 & 6 min & 0.2 Kb & 4.87 Kb & 34.12 Kb & 136.5 Kb & 1.6 Mb\\\hline 
        5 & 15 min & 1.0 Kb & 24.37 Kb & 170.62 Kb & 682.5 Kb & 7.99 Mb\\\hline
        \end{tabular}
        \caption{Estimated data volume produced by the RTC's YSI sondes}
      \end{center}
\end{table}

@@

In conclusion, after detailing the SF-BEAMS sensor network, and describing the 
infrastructure of NetBEAMS, its the motivation and goals for this project were 
presented. The next chapter is the actual analysis of existing database systems 
mentioned in Chapter 2, which aligns with the requirements and characteristics of 
NetBEAMS. Meanwhile, more details regarding the architecture of NetBEAMS, as well as
the development guidelines can be found in the appendix of Chapter 10.
